\SetValue{SectionAB}{}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%

\begin{center}
    \begin{tabular}{|c|c|c|c|c|}
        \hline
        $t$  (minutes) & 0 & 3 & 7 & 12 \\ 
        \hline
        $C(t)$  (degrees Celsius) & 100 & 85 & 69 & 55 \\
        \hline
    \end{tabular}
\end{center}
    
The temperature of coffee in a cup at time $t$ minutes is modeled by a decreasing differentiable function $C$, where $C(t)$ is measured in degrees Celsius. For $0 \leq t \leq 12$, selected values of $C(t)$ are given in the table shown.
    
(d) For the model defined in part (c), it can be shown that $C^{\prime \prime}(t)=\frac{0.2455 e^{0.01 t}(100-t)}{t^2}$. For $12<t<20$, determine whether the temperature of the coffee is changing at a decreasing rate or at an increasing rate.
            
Give a reason for your answer.
}\SetValue{Solution}{%

Because $C^{\prime \prime}(t)>0$ on the interval $12<t<20$, the rate of change in the temperature of the coffee, $C^{\prime}(t)$, is increasing on this interval.

That is, on the interval $12<t<20$, the temperature of the coffee is changing at an increasing rate.

}\SetValue{Rubric}{%

# General Scoring Notes

The model solution is presented using standard mathematical notation.

Answers (numeric or algebraic) need not be simplified. Answers given as a decimal approximation should be correct to three places after the decimal point. Within each individual free-response question, at most one point is not earned for inappropriate rounding.

| $t$ <br> (minutes) | 0 | 3 | 7 | 12 |
| :---: | :---: | :---: | :---: | :---: |
| $C(t)$ <br> (degrees Celsius) | 100 | 85 | 69 | 55 |

The temperature of coffee in a cup at time $t$ minutes is modeled by a decreasing differentiable function $C$, where $C(t)$ is measured in degrees Celsius. For $0 \leq t \leq 12$, selected values of $C(t)$ are given in the table shown.

## Model Solution (d)

Because $C^{\prime \prime}(t)>0$ on the interval $12<t<20$, the rate of change in the temperature of the coffee, $C^{\prime}(t)$, is increasing on this interval.

That is, on the interval $12<t<20$, the temperature of the coffee is changing at an increasing rate.

## Scoring (d)

- For Because $C^{\prime \prime}(t)>0$ on the interval $12<t<20$, the rate of change in the temperature of the coffee, $C^{\prime}(t)$, is increasing on this interval.

That is, on the interval $12<t<20$, the temperature of the coffee is changing at an increasing rate.

    - Answer with reason; 1 point

## Scoring notes (d)

- This point is earned only for a correct answer with a correct reason that references the sign of the second derivative of $C$.

- A response that provides a reason based on the evaluation of $C^{\prime \prime}(t)$ at a single point does not earn this point.

- A response that uses ambiguous pronouns (such as ``It is positive, so increasing") does not earn this point.

- A response does not need to reference the interval $12<t<20$ to earn the point.

Total for part (d) 1 point
}\SetValue{Answer}{%

}
\ProcessDATA


