\SetValue{SectionAB}{}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%

A particle moving along a curve in the $x y$-plane has position $(x(t), y(t))$ at time $t$ seconds, where $x(t)$ and $y(t)$ are measured in centimeters. It is known that $x^{\prime}(t)=8 t-t^2$ and $y^{\prime}(t)=-t+\sqrt{t^{1.2}+20}$. At time $t=2$ seconds, the particle is at the point $(3,6)$.

(a) Find the speed of the particle at time $t=2$ seconds. Show the setup for your calculations.

}\SetValue{Solution}{%

$\sqrt{\left(x^{\prime}(2)\right)^2+\left(y^{\prime}(2)\right)^2}$

$=12.3048506$

The speed of the particle at time $t=2$ seconds is 12.305 (or 12.304) centimeters per second.

}\SetValue{Rubric}{%

# General Scoring Notes

The model solution is presented using standard mathematical notation.

Answers (numeric or algebraic) need not be simplified. Answers given as a decimal approximation should be correct to three places after the decimal point. Within each individual free-response question, at most one point is not earned for inappropriate rounding.

A particle moving along a curve in the $x y$-plane has position $(x(t), y(t))$ at time $t$ seconds, where $x(t)$ and $y(t)$ are measured in centimeters. It is known that $x^{\prime}(t)=8 t-t^2$ and $y^{\prime}(t)=-t+\sqrt{t^{1.2}+20}$. At time $t=2$ seconds, the particle is at the point $(3,6)$.

## Model Solution (a)

$\sqrt{\left(x^{\prime}(2)\right)^2+\left(y^{\prime}(2)\right)^2}$

$=12.3048506$

The speed of the particle at time $t=2$ seconds is 12.305 (or 12.304) centimeters per second.

## Scoring (a)

- For $\sqrt{\left(x^{\prime}(2)\right)^2+\left(y^{\prime}(2)\right)^2}$
     - Setup for speed; 1 point

- For $=12.3048506$ or $12.305$ or $12.304$
    - Answer; 1 point

## Scoring notes (a)

- The first point is carned for the expression $\sqrt{\left(x^{\prime}(2)\right)^2+\left(y^{\prime}(2)\right)^2} \cdot \sqrt{\left(x^{\prime}(t)\right)^2+\left(y^{\prime}(t)\right)^2}$, or equivalent.

- A response that presents just the exact answer. $\sqrt{144+\left(-2+\sqrt{2^{1.2}+20}\right)^2}$, earns both points.

- The second point is earned only for the answer 12.305 (or 12.304 ) regardless of whether the first point is eamed.

- A response that includes a linkage error, such as

$$
\sqrt{\left(x^{\prime}(t)\right)^2+\left(y^{\prime}(t)\right)^2}=\sqrt{144+\left(-2+\sqrt{2^{1.2}+20}\right)^2} \text { or } \sqrt{\left(x^{\prime}(t)\right)^2+\left(y^{\prime}(t)\right)^2}=12.305(\text { or } 12.304)
$$
 earns at most 1 of the 2 points.

- Missing or incorrect units will not affect scoring in this part.

Total for part (a) 2 points

}\SetValue{Answer}{%

}
\ProcessDATA


