\SetValue{SectionAB}{}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%

A particle moving along a curve in the $x y$-plane has position $(x(t), y(t))$ at time $t$ seconds, where $x(t)$ and $y(t)$ are measured in centimeters. It is known that $x^{\prime}(t)=8 t-t^2$ and $y^{\prime}(t)=-t+\sqrt{t^{1.2}+20}$. At time $t=2$ seconds, the particle is at the point $(3,6)$.

(b) Find the total distance traveled by the particle over the time interval $0 \leq t \leq 2$. Show the setup for your calculations.

}\SetValue{Solution}{%

$$
\begin{aligned}
& \int_0^2 \sqrt{\left(x^{\prime}(t)\right)^2+\left(y^{\prime}(t)\right)^2} d t \\
& =15.901715
\end{aligned}
$$


The total distance traveled by the particle over the time interval $0 \leq t \leq 2$ is 15.902 (or 15.901 ) centimeters.

}\SetValue{Rubric}{%

# General Scoring Notes

The model solution is presented using standard mathematical notation.

Answers (numeric or algebraic) need not be simplified. Answers given as a decimal approximation should be correct to three places after the decimal point. Within each individual free-response question, at most one point is not earned for inappropriate rounding.

A particle moving along a curve in the $x y$-plane has position $(x(t), y(t))$ at time $t$ seconds, where $x(t)$ and $y(t)$ are measured in centimeters. It is known that $x^{\prime}(t)=8 t-t^2$ and $y^{\prime}(t)=-t+\sqrt{t^{1.2}+20}$. At time $t=2$ seconds, the particle is at the point $(3,6)$.

## Model Solution (b)

$\int_0^2 \sqrt{\left(x^{\prime}(t)\right)^2+\left(y^{\prime}(t)\right)^2} d t=15.901715$

The total distance traveled by the particle over the time interval $0 \leq t \leq 2$ is 15.902 (or 15.901) centimeters.

## Scoring (b)

- For $\int_0^2 \sqrt{\left(x^{\prime}(t)\right)^2+\left(y^{\prime}(t)\right)^2} d t$
    - Integral; 1 point

- For $15.901715$ or $15.902$ or $15.901$    
    - Answer; 1 point

The total distance traveled by the particle over the time interval $0 \leq t \leq 2$ is 15.902 (or 15.901) centimeters.

## Scoring notes (b)

- The first point is earned only for an integral of $\int_0^2 \sqrt{\left(x^{\prime}(t)\right)^2+\left(y^{\prime}(t)\right)^2} d t$ (or the mathematical equivalent), with or without the differential.

- Note: $\int_0^2 \sqrt{x^{\prime}(t)^2+y^{\prime}(t)^2} d t$ is not read as a parenthesis error.

- The second point is earned only for an answer of 15.902 (or 15.901 ), regardless of whether the first point is carned.

- Missing or incorrect units will not affect scoring in this part.

Total for part (b) 2 points

}\SetValue{Answer}{%

}
\ProcessDATA


