\SetValue{SectionAB}{}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%

A particle moving along a curve in the $x y$-plane has position $(x(t), y(t))$ at time $t$ seconds, where $x(t)$ and $y(t)$ are measured in centimeters. It is known that $x^{\prime}(t)=8 t-t^2$ and $y^{\prime}(t)=-t+\sqrt{t^{1.2}+20}$. At time $t=2$ seconds, the particle is at the point $(3,6)$.

(c) Find the $y$-coordinate of the position of the particle at the time $t=0$. Show the setup for your calculations.

}\SetValue{Solution}{%

$$
y(0)=6+\int_2^0 y^{\prime}(t) d t=6-7.173613=-1.173613
$$


The $y$-coordinate of the position of the particle at time $t=0$ is $-1.174($ or -1.173$)$

}\SetValue{Rubric}{%

# General Scoring Notes

The model solution is presented using standard mathematical notation.

Answers (numeric or algebraic) need not be simplified. Answers given as a decimal approximation should be correct to three places after the decimal point. Within each individual free-response question, at most one point is not earned for inappropriate rounding.

A particle moving along a curve in the $x y$-plane has position $(x(t), y(t))$ at time $t$ seconds, where $x(t)$ and $y(t)$ are measured in centimeters. It is known that $x^{\prime}(t)=8 t-t^2$ and $y^{\prime}(t)=-t+\sqrt{t^{1.2}+20}$. At time $t=2$ seconds, the particle is at the point $(3,6)$.

## Model Solution (c)

$$
y(0)=6+\int_2^0 y^{\prime}(t) d t=6-7.173613=-1.173613
$$


The $y$-coordinate of the position of the particle at time $t=0$ is $-1.174($ or -1.173$)$

## Scoring (c)

- For $y(0)=6+\int_2^0 y^{\prime}(t) d t=6-7.173613=-1.173613$
    - Definite integral; 1 point
    - Uses initial condition; 1 point

- For The $y$-coordinate of the position of the particle at time $t=0$ is $-1.174($ or -1.173$)$
    - Answer; 1 point

## Scoring notes (c)

- An answer of -1.174 (or -1.173 ) with no supporting work does not earn any points.

- The first point is earned for either of the definite integrals $\int_2^0 y^{\prime}(t) d t$ or $\int_0^2 y^{\prime}(t) d t$.

- The second point is earned for any of:
    - $y(2) \pm \int_2^0 y^{\prime}(t) d t, 6 \pm \int_2^0 y^{\prime}(t) d t$,

    - $y(2) \pm \int_0^2 y^{\prime}(t) d t, 6 \pm \int_0^2 y^{\prime}(t) d t$,

    - $y(2) \pm 7.173613$, or $6 \pm 7.173613$.
- A response that attempts to evaluate $\int y^{\prime}(t) d t$ does not earn the first or the third point.
    - Such a response can earn the second point by attempting to solve for the constant of integration by presenting an expression as an antiderivative for $y^{\prime}(t)$, evaluating this expression at $t=2$, and setting this expression equal to 6.

- A response that reverses the limits of integration, e.g. $y(0)=6+\int_0^2 y^{\prime}(t) d t$ or $6+7.173613$, earns the second point but does not earn the third point.

- In order to carn the third point, a response must have carned at least 1 of the first 2 points.

- A response containing any linkage error can earn at most 2 of the 3 points. For example:
    - Equating two uncqual quantities: $\int_2^0 y^{\prime}(t) d t=-1.174, \int_2^0 y^{\prime}(t) d t=6-7.173613$,
    
    $$
    6+\int_0^2 y^{\prime}(t) d t=6-7.173613, \text { or } 6+\int_0^2 y^{\prime}(t) d t=6+7.173613=-1.173613
    $$
    
    - Equating an expression to a numerical value: $y(t)=6+\int_2^0 y^{\prime}(t) d t=-1.174$
- Missing differentials (dt):
    - Unambiguous responses of $y(2)+\int_2^0 y^{\prime}(t), y(2)-\int_0^2 y^{\prime}(t), 6+\int_2^0 y^{\prime}(t)$, or $6-\int_0^2 y^{\prime}(t)$ carn the first 2 points and would carn the third point for the correct numerical answer.

    - Unambiguous responses of $y(2)+\int_0^2 y^{\prime}(t)$ or $6+\int_0^2 y^{\prime}(t)$ with reversed limits of integration and missing differential eam the first 2 points but cannot carn the third point.

    - Ambiguous responses of $\int_2^0 y^{\prime}(t)+y(2),-\int_0^2 y^{\prime}(t)+y(2), \int_2^0 y^{\prime}(t)+6$, or $-\int_0^2 y^{\prime}(t)+6$ earn the first point, do not earn the second point, but do earn the third point if a correct numeric answer is provided. If no numeric answer is given, none of these responses earn the third point.

    - Ambiguous responses of $\int_0^2 y^{\prime}(t)+y(2)$ or $\int_0^2 y^{\prime}(t)+6$ with reversed limits of integration and no differential carn 1 out of 3 points.

- If a response provides work for both the $x$ - and $y$-coordinates, the work for the $x$-coordinate will not affect scoring.

- However, a response that reports only a completely correct $x$-coordinate of the particle's position at time $t=0$ with all supporting work, e.g., $x(0)=3+\int_2^0 x^{\prime}(t) d t=-\frac{31}{3}=-10.333$, earns 2 out of 3 points.

Total for part (c) 3 points

}\SetValue{Answer}{%

}
\ProcessDATA


