\SetValue{SectionAB}{}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%

The Maclaurin series for a function $f$ is given by $\sum_{n=1}^{\infty} \frac{(n+1) x^n}{n^2 6^n}$ and converges to $f(x)$ for all $x$ in the interval of convergence. It can be shown that the Maclaurin series for $f$ has a radius of convergence of 6.

(a) Determine whether the Maclaurin series for $f$ converges or diverges at $x=6$. Give a reason for your answer.

}\SetValue{Solution}{%

At $x=6$, the series is $\sum_{n=1}^{\infty} \frac{(n+1) 6^n}{n^2 6^n}=\sum_{n=1}^{\infty} \frac{n+1}{n^2}$.

Because $\frac{n+1}{n^2}>\frac{1}{n}$ for all $n \geq 1$ and the harmonic series $\sum_{n=1}^{\infty} \frac{1}{n}$ diverges, the series $\sum_{n=1}^{\infty} \frac{n+1}{n^2}$ diverges by the comparison test.

}\SetValue{Rubric}{%

# General Scoring Notes

The model solution is presented using standard mathematical notation.

Answers (numeric or algebraic) need not be simplified. Answers given as a decimal approximation should be correct to three places after the decimal point. Within each individual free-response question, at most one point is not earned for inappropriate rounding.

The Maclaurin series for a function $f$ is given by $\sum_{n=1}^{\infty} \frac{(n+1) x^n}{n^2 6^n}$ and converges to $f(x)$ for all $x$ in the interval of convergence. It can be shown that the Maclaurin series for $f$ has a radius of convergence of 6.

## Model Solution (a)

At $x=6$, the series is $\sum_{n=1}^{\infty} \frac{(n+1) 6^n}{n^2 6^n}=\sum_{n=1}^{\infty} \frac{n+1}{n^2}$.

Because $\frac{n+1}{n^2}>\frac{1}{n}$ for all $n \geq 1$ and the harmonic series $\sum_{n=1}^{\infty} \frac{1}{n}$ diverges, the series $\sum_{n=1}^{\infty} \frac{n+1}{n^2}$ diverges by the comparison test.

## Scoring (a)

- For At $x=6$, the series is $\sum_{n=1}^{\infty} \frac{(n+1) 6^n}{n^2 6^n}=\sum_{n=1}^{\infty} \frac{n+1}{n^2}$.
   - Considers $\frac{(n+1) 6^n}{n^2 6^n}$; 1 point

-For Because $\frac{n+1}{n^2}>\frac{1}{n}$ for all $n \geq 1$ and the harmonic series $\sum_{n=1}^{\infty} \frac{1}{n}$ diverges, the series $\sum_{n=1}^{\infty} \frac{n+1}{n^2}$ diverges by the comparison test.
   - Answer with reason; 1 point

## Scoring notes (a)

- To earn the first point using either the comparison or limit comparison test, a response must consider the $\operatorname{term} \frac{(n+1) 6^n}{n^2 6^n}$. This could be shown by considering the term $\frac{n+1}{n^2}$, either individually or as part of a sum.

- To earn the second point using the comparison test a response must demonstrate that the terms $\frac{n+1}{n^2}$ are larger than the terms in a divergent series.

- $-\frac{n+1}{n^2}>\frac{1}{n}$, diverges ${ }^{-1}$ carns both points.

- The response does not need to use the term ``comparison test," but the response cannot declare use of an incorrect test.

- Alternate solution (limit comparison test):

At $x=6$, the series is $\sum_{n=1}^{\infty} \frac{(n+1) 6^n}{n^2 6^n}=\sum_{n=1}^{\infty} \frac{n+1}{n^2}$.
Because $\lim _{n \rightarrow \infty} \frac{\frac{n+1}{n^2}}{\frac{1}{n}}=\lim _{n \rightarrow \infty} \frac{n^2+n}{n^2}=1$ and the harmonic series $\sum_{n=1}^{\infty} \frac{1}{n}$ diverges, the series $\sum_{n=1}^{\infty} \frac{n+1}{n^2}$ diverges by the limit comparison test.

- To earn the second point using the limit comparison test, a response must correctly write the limit of the ratio of the terms in the given series to the terms of a divergent series and demonstrate that the limit of this ratio is 1.

- The response does not need to use the term ``limit comparison test," but the response cannot declare use of an incorrect test.

Total for part (a) 2 points

}\SetValue{Answer}{%

}
\ProcessDATA


