\SetValue{SectionAB}{}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%

The Maclaurin series for a function $f$ is given by $\sum_{n=1}^{\infty} \frac{(n+1) x^n}{n^2 6^n}$ and converges to $f(x)$ for all $x$ in the interval of convergence. It can be shown that the Maclaurin series for $f$ has a radius of convergence of 6.

(d) Let $g(x)=\sum_{n=1}^{\infty} \frac{(n+1) x^{2 n}}{n^2 3^n}$. Use the ratio test to determine the radius of convergence of the Maclaurin series for $g$.

}\SetValue{Solution}{%
 
}\SetValue{Rubric}{%

# General Scoring Notes

The model solution is presented using standard mathematical notation.

Answers (numeric or algebraic) need not be simplified. Answers given as a decimal approximation should be correct to three places after the decimal point. Within each individual free-response question, at most one point is not earned for inappropriate rounding.

The Maclaurin series for a function $f$ is given by $\sum_{n=1}^{\infty} \frac{(n+1) x^n}{n^2 6^n}$ and converges to $f(x)$ for all $x$ in the interval of convergence. It can be shown that the Maclaurin series for $f$ has a radius of convergence of 6.

## Model Solution (d)

$\left|\frac{\frac{(n+2) x^{2 n+2}}{(n+1)^2 3^{n+1}}}{\frac{(n+1) x^{2 n}}{n^2 3^n}}\right|=\left|\frac{(n+2) x^{2 n+2}}{(n+1)^2 3^{n+1}} \cdot \frac{n^2 3^n}{(n+1) x^{2 n}}\right|$

$\lim _{n \rightarrow \infty}\left|\frac{(n+2) n^2}{(n+1)^3}\right| \cdot\left|\frac{x^2}{3}\right|=\left|\frac{x^2}{3}\right|$

$$
\left|\frac{x^2}{3}\right|<1 \Rightarrow x^2<3 \Rightarrow|x|<\sqrt{3}
$$


The radius of convergence of $g$ is $\sqrt{3}$.

## Scoring (d)

- For $\left|\frac{\frac{(n+2) x^{2 n+2}}{(n+1)^2 3^{n+1}}}{\frac{(n+1) x^{2 n}}{n^2 3^n}}\right|=\left|\frac{(n+2) x^{2 n+2}}{(n+1)^2 3^{n+1}} \cdot \frac{n^2 3^n}{(n+1) x^{2 n}}\right|$
    - Sets up ratio; 1 point

- For  $\lim _{n \rightarrow \infty}\left|\frac{(n+2) n^2}{(n+1)^3}\right| \cdot\left|\frac{x^2}{3}\right|=\left|\frac{x^2}{3}\right|$  
    - Limit; 1 point

- For $\left|\frac{x^2}{3}\right|<1 \Rightarrow x^2<3 \Rightarrow|x|<\sqrt{3}$. The radius of convergence of $g$ is $\sqrt{3}$.
    - Radius of convergence; 1 point

## Scoring notes (d)

- The first point is earned by presenting a correct ratio with or without absolute values. Once earned. this point cannot be lost. Any errors in simplification or evaluation of the limit will not earn the second point.

- The first point is carned for ratios mathematically equivalent to any of the following:

$$
\frac{\frac{(n+2) x^{2 n+2}}{(n+1)^2 3^{n+1}}}{\frac{(n+1) x^{2 n}}{n^2 3^n}}, \frac{(n+2) x^{2 n+2}}{(n+1)^2 3^{n+1}} \cdot \frac{n^2 3^n}{(n+1) x^{2 n}}, \frac{\frac{(n+1) x^{2 n}}{n^2 3^n}}{\frac{n x^{2 n-2}}{(n-1)^2 3^{n-1}}} \text {, or } \frac{(n+1) x^{2 n}}{n^2 3^n} \cdot \frac{(n-1)^2 3^{n-1}}{n x^{2 n-2}}
$$

- The first point is also earned for ratios mathematically equivalent to the following reciprocal ratios:

$$
\frac{\frac{(n+1) x^{2 n}}{n^2 3^n}}{\frac{(n+2) x^{2 n+2}}{(n+1)^2 3^{n+1}}}, \frac{(n+1) x^{2 n}}{n^2 3^n} \cdot \frac{(n+1)^2 3^{n+1}}{(n+2) x^{2 n+2}}, \frac{\frac{n x^{2 n-2}}{(n-1)^2 3^{n-1}}}{\frac{(n+1) x^{2 n}}{n^2 3^n}}, \text { or } \frac{n x^{2 n-2}}{(n-1)^2 3^{n-1}} \cdot \frac{n^2 3^n}{(n+1) x^{2 n}}
$$

    Responses including any of these reciprocal ratios can earn the second point for using limit notation to correctly find a limit of the absolute value of their ratio to be $\left|\frac{3}{x^2}\right|$. Such responses earn the third point only for a final answer of $\sqrt{3}$ with a valid explanation for reporting the reciprocal of $\frac{1}{\sqrt{3}}$.

- To earn the second point a response must use the ratio and correctly evaluate the limit of the ratio, using correct limit notation.

- The third point is earned only for an answer of $\sqrt{3}$ with supporting work.

Total for part (d) 3 points

}\SetValue{Answer}{%

}
\ProcessDATA


