\SetValue{Module}{1}\SetValue{SectionAB}{A}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%%
    
Jordan owns 15 pairs of sneakers. Three fifths of the pairs are red and the rest are white. Two thirds of the pairs are high-top and the rest are low-top. The red high-top sneakers make up a fraction of the collection. What is the least possible value of this fraction?

\ansFIVEs{%start
		0 }{%<--- (A)
		\frac{1}{5} }{%<--- (B)
		\frac{4}{15} }{%<--- (C)
		\frac{1}{3} }{%<---- (D)
		\frac{2}{5} }%<---- (D)
}\SetValue{Concept}{%



}\SetValue{AltText}{%



}\SetValue{Solution}{%

Solution 1
Jordan has 10 high top sneakers, and 6 white sneakers. We would want as many white hightop sneakers as possible, so we set 6 high-top sneakers to be white. Then, we have $10-6=4$ red high-top sneakers, so the answer is $\frac{4}{15}$.

Solution 2
We first start by finding the amount of red and white sneakers. 3/5 * 15=9 red sneakers, so 6 are white sneakers. Then $2 / 3$ * 15=10 are high top sneakers, so 5 are low top sneakers. Now think about 15 slots and the first 10 are labeled high top sneakers. if we insert the last 5 sneakers as red sneakers there are 4 leftover over red sneakers. Putting those four sneakers as high top sneakers we have our answer as C, or $\frac{4}{15}$.
-ermwhatthesigma
Solution 3
There are $\frac{3}{5} \cdot 15=9$ red pairs of sneakers and 6 white pairs. There are also $\frac{2}{3} \cdot 15=10$ high-top pairs of sneakers and 5 low-top pairs. Let $r$ be the number of red high-top sneakers and let $w$ be the number of white high-top sneakers. It follows that there are $9-r$ red pairs of low-top sneakers and $6-r$ white pairs. II We must have $9-r \leq 5$, in order to have a valid amount of white sneakers. Solving this inequality gives $r \geq 4$, so the smallest possible value for $r$ is 4 . This means that there would be $9-4=5$ pairs of low-top red sneakers, so there are 0 pairs of low-top white sneakers and 6 pairs of high top white sneakers. This checks out perfectly, so the smallest fraction is
(C) $\frac{4}{15}$.
}\SetValue{Rubric}{%Markdown



}\SetValue{Hint}{%
Solution Goes Here
}\SetValue{Answer}{%

}
\ProcessDATA



