\SetValue{SectionAB}{}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%

A company is planning to hire both male and female employees for a new project. The company wants to hire at least twice as many men as women for the project. The company will spend no more than $\$5000$ on the salaries for these new hires. Each man hired will cost the company $\$1250$, and each woman will cost $\$1000$. Let $m$ represent the number of men hired and $w$ represent the number of women hired, where $m$ and $w$ are nonnegative integers. Which of the following systems of inequalities best expresses this situation?

\ansFOURs{%start
\begin{cases}m \geq 2w\\
1250m + 1000w \leq 5000\end{cases}}{%<--- (A)
\begin{cases}2m \geq w\\
1250m + 1000w \leq 5000\end{cases}}{%<--- (B)
\begin{cases}m \geq 2w\\
1250m + 500w \leq 5000\end{cases}}{%<--- (C)
\begin{cases}2m \geq w\\
1250m + 500w \leq 5000\end{cases}}%<---- (D)

}\SetValue{Solution}{%

Given the problem, we need to set up the inequalities that represent the conditions described.

1. The company wants to hire at least twice as many men as women. This can be expressed as: \(m \geq 2w\)

2. The total spending on salaries should not exceed \$5000. Since each man costs \$1250 and each woman costs \$1000, the inequality for the total cost is: \(1250m + 1000w \leq 5000\)   

Now, let's evaluate each option:

%\begin{enumerate}[label={\textbf{(\Alph*)}}]
1. \( m \geq 2w \) and \( 1250m + 1000w \leq 5000 \): **True**.    
    
    This matches the conditions given in the problem.

2. \( 2m \geq w \) and \( 1250m + 1000w \leq 5000 \):  **False**.

    The inequality \( 2m \geq w \) does not match the requirement of having at least twice as many men as women.

3. \( m \geq 2w \) and \( 1250m + 500w \leq 5000 \):  **False**.

    The salary cost for women is incorrect; it should be \(\$1000\) per woman, not \(\$500\).

4. \( 2m \geq w \) and \( 1250m + 500w \leq 5000 \):  **False**.
    
    Both the ratio condition and the salary cost for women are incorrect.
%\end{enumerate}

Thus, the correct system of inequalities is option $\fbox{A}$.

}\SetValue{Answer}{%
B
}
\ProcessDATA


