\SetValue{Module}{1}\SetValue{SectionAB}{A}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%%
    
Tyler is tiling the floor of his 12 foot by 16 foot living room. He plans to place one-foot by one-foot square tiles to form a border along the edges of the room and to fill in the rest of the floor with two-foot by two-foot square tiles. How many tiles will he use?

\ansFIVEs{%start
		48 }{%<--- (A)
		87 }{%<--- (B)
		91 }{%<--- (C)
		96 }{%<---- (D)
		120 }%<---- (D)
}\SetValue{Concept}{%



}\SetValue{AltText}{%



}\SetValue{Solution}{%

Answer (B): The perimeter of the room is $2(12+16)=56$ feet. The 4 corner tiles each occupy 2 feet of the perimeter, so Tyler needs those 4 plus another $56-4 \cdot 2=48$ one-foot square tiles to make the border. The remaining space in the room is a 10 foot by 14 foot rectangle, so Tyler needs $\frac{10}{2} \cdot \frac{14}{2}=35$ two-foot square tiles to cover it. Therefore he needs a total of $4+48+35=87$ tiles.

OR
If Tyler used only one-foot square tiles, he would need a total of $12 \cdot 16=192$ tiles. As above, the room minus the border is a 10 foot by 14 foot rectangle to be covered with two-foot square tiles, each of which has the same area as 4 one-foot square tiles. Therefore the number of tiles needed to cover that portion of the room is not $10 \cdot 14=140$, but $\frac{140}{4}=35$, and the total number of tiles needed is $(192-140)+35=87$.

}\SetValue{Rubric}{%Markdown



}\SetValue{Hint}{%
Solution Goes Here
}\SetValue{Answer}{%

}
\ProcessDATA



