\SetValue{Module}{1}\SetValue{SectionAB}{A}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%%
    
Bella begins to walk from her house toward her friend Ella's house. At the same time, Ella begins to ride her bicycle toward Bella's house. They each maintain a constant speed, and Ella rides 5 times as fast as Bella walks. The distance between their houses is 2 miles, which is 10,560 feet, and Bella covers $2 \frac{1}{2}$ feet with each step. How many steps will Bella take by the time she meets Ella?

\ansFIVEs{%start
		704 }{%<--- (A)
		845 }{%<--- (B)
		1056 }{%<--- (C)
		1760 }{%<---- (D)
		3520 }%<---- (D)
}\SetValue{Concept}{%

벨라는 자신의 집에서 친구 엘라의 집을 향해 걷기 시작합니다. 동시에 엘라는 자전거를 타고 벨라의 집을 향해 달려가기 시작합니다. 두 사람은 각각 일정한 속도를 유지하며, 엘라는 벨라가 걷는 속도보다 5배 빠른 속도로 자전거를 탑니다. 두 집 사이의 거리는 2마일, 즉 10,560피트이며, 벨라는 한 발자국씩 $2 \frac{1}{2}$ 피트를 이동합니다. 벨라는 엘라를 만날 때까지 몇 걸음을 걸을까요?

풀이
1. 속도 관계 파악
- 벨라(Bella)의 보행 속도를 $v$ 라고 하면,

엘라(Ella)의 자전거 속도는 $5 v$ 입니다.
2. 두 사람이 만날 때까지 이동한 거리 비율
- 두 사람은 동시에 출발하여 서로를 향해 움직이므로, 같은 시간 $t$ 동안 이동한 거리의 합이 집 간 거리 10560 피트가 됩니다.
- 이동 거리 비는 속도 비와 같으므로

$$
\text { Bella : Ella }=v: 5 v=1: 5 .
$$


즉, 전체 거리 10560 피트 중
- 벨라는 $\frac{1}{1+5}=\frac{1}{6}$
- 엘라는 $\frac{5}{1+5}=\frac{5}{6}$ 를 각각 이동합니다.
3. 벨라가 실제로 걸은 거리

$$
\frac{1}{6} \times 10560=1760 \text { 피트. }
$$

4. 걸음 한 걸음당 이동 거리
- 문제에서 벨라는 한 걸음에 $2 \frac{1}{2}=\frac{5}{2}$ 피트를 이동합니다.
5. 총 걸음 수 계산

$$
\text { 걸음 수 }=\frac{\text { 벨라가 걸은 총거리 }}{\text { 한 걸음 거리 }}=\frac{1760}{\frac{5}{2}}=1760 \times \frac{2}{5}=704 .
$$


따라서 벨라가 엘라를 만날 때까지 걸을 총 걸음 수는 704걸음입니다.
}\SetValue{AltText}{%


}\SetValue{Solution}{%

1. Relate their speeds

Let Bella's walking speed be $v \mathrm{ft} / \mathrm{s}$.
Ella rides $5 v \mathrm{ft} / \mathrm{s}$, because she is 5 times as fast.
2. Partition the total distance

They start at the same moment and travel toward each other.
In the same time $t$, the distances they cover are in the same ratio as their speeds:

$$
\text { Bella : Ella }=v: 5 v=1: 5 .
$$


Hence of the 10560 ft between the houses,
- Bella covers $\frac{1}{1+5}=\frac{1}{6}$,
- Ella covers $\frac{5}{1+5}=\frac{5}{6}$.
3. Distance walked by Bella

$$
\text { Bella's distance }=\frac{1}{6} \times 10560=1760 \text { feet. }
$$

4. Convert distance to steps

Bella travels $2 \frac{1}{2}=\frac{5}{2} \mathrm{ft}$ with each step.
Therefore,

$$
\text { number of steps }=\frac{1760}{\frac{5}{2}}=1760 \times \frac{2}{5}=704 .
$$

704
}\SetValue{Solution MAA}{%

Answer (A): By the time that the two girls meet, Ella will ride 5 times the distance that Bella walks, so Ella will ride $\frac{5}{6}$ of the total distance, and Bella will walk $\frac{1}{6}$ of the total distance, or $\frac{1}{6}(10,560)=1760$ feet. Each of her steps covers $2 \frac{1}{2}=\frac{5}{2}$ feet, so the number of steps she will take is $1760 \div \frac{5}{2}=1760 \cdot \frac{2}{5}=704$.

OR

Bella's rate is 2.5 feet per step whereas Ella travels 12.5 feet for each of Bella's steps. So together they travel 15 feet for each of Bella's steps. Hence the number of steps taken by Bella when she meets Ella is $\frac{10,560}{15}=704$.

}\SetValue{Rubric}{%Markdown



}\SetValue{Hint}{%
Solution Goes Here
}\SetValue{Answer}{%

}
\ProcessDATA



