\SetValue{Module}{1}\SetValue{SectionAB}{A}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%%
    
Two ships A and B leaves a port simultaneously. A steams at $10 \mathrm{kmh}^{-1}$ on a bearing of $160^{\circ}$ and $B$ steams on a bearing of $215^{\circ}$. Just after one hour the bearing of $B$ from $\mathbf{A}$ is $260^{\circ}$. Find the speed of $\mathbf{B}$, correct to two significant figures.

}\SetValue{Concept}{%



}\SetValue{AltText}{%



}\SetValue{Solution}{%

1. Define Positions after 1 Hour:

- Let the port be the origin $\mathrm{P}(0,0)$.

- Ship A travels at $10 \mathrm{kmh}^{-1}$ for 1 hour on a bearing of $160^{\circ}$. The distance PA is $10 \times 1=10$ km.

- Ship B travels at an unknown speed $v \mathrm{kmh}^{-1}$ for 1 hour on a bearing of $215^{\circ}$. The distance PB is $v \times 1=v \mathrm{~km}$.

2. Visualize the Triangle:

- We have a triangle PAB formed by the Port (P), Ship A's position after 1 hour (A), and Ship B's position after 1 hour (B).

- Side PA = 10 km.

- Side $\mathrm{PB}=v \mathrm{~km}$ (this is what we need to find, as $v$ is the speed).

- Side $A B$ is the distance between the ships after 1 hour.

3. Calculate the Angles of the Triangle PAB:

- Angle APB: This is the angle at the port between the paths of the two ships. Angle APB = Bearing of $B$ - Bearing of $A=215^{\circ}-160^{\circ}=55^{\circ}$.

- Angle PAB: We need to use the bearing of B from $\mathrm{A}\left(260^{\circ}\right)$.

- First, find the bearing of $P$ from $A$. If the bearing of $A$ from $P$ is $160^{\circ}$, the bearing of $P$ from $A$ is $160^{\circ}+180^{\circ}=340^{\circ}$.

- The bearing of $B$ from $A$ is $260^{\circ}$.

- The angle PAB, inside the triangle, is the difference between the bearing of $P$ from $A$ and the bearing of $B$ from $A$.

- Angle $P A B=$ Bearing of $P$ from $A-$ Bearing of $B$ from $A=340^{\circ}-260^{\circ}=80^{\circ}$.

- Angle PBA: The sum of angles in a triangle is $180^{\circ}$. Angle $\mathrm{PBA}=180^{\circ}$ - Angle APB - Angle PAB Angle PBA $=180^{\circ}-55^{\circ}-80^{\circ}=45^{\circ}$.

4. Use the Sine Rule:

Now we have a triangle PAB with all angles known and one side (PA = 10 km ). We want to find the length of side PB (which is $v$ ). The Sine Rule states:

$$
\frac{a}{\sin A}=\frac{b}{\sin B}=\frac{c}{\sin C}
$$


Applying this to triangle PAB:

$$
\frac{P A}{\sin (\angle P B A)}=\frac{P B}{\sin (\angle P A B)}
$$

Substituting the known values:

$$
\frac{10}{\sin \left(45^{\circ}\right)}=\frac{v}{\sin \left(80^{\circ}\right)}
$$

5. Solve for v:

$$
v=\frac{10 \times \sin \left(80^{\circ}\right)}{\sin \left(45^{\circ}\right)}
$$


Using calculator values:

- $\sin \left(80^{\circ}\right) \approx 0.98480775$

- $\sin \left(45^{\circ}\right)=\frac{\sqrt{2}}{2} \approx 0.70710678$

$$
v \approx \frac{10 \times 0.98480775}{0.70710678} \approx \frac{9.8480775}{0.70710678} \approx 13.92717
$$

6. Round to Two Significant Figures:

The value is approximately 13.92717.

- The first significant figure is 1.

- The second significant figure is 3.

- The next digit is 9 , which is 5 or greater, so we round up the second significant figure (3 becomes 4). $v \approx 14$

The speed of ship B is approximately $14 \mathrm{kmh}^{-1}$.

}\SetValue{Rubric}{%Markdown



}\SetValue{Hint}{%
Solution Goes Here
}\SetValue{Answer}{%

}
\ProcessDATA



