\SetValue{Module}{1}\SetValue{SectionAB}{A}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%%
    
A boat is rowed at a speed of $8 \mathrm{kmh}^{-1}$ straight across a river, which is flowing at a speed of $6 \mathrm{kmh}^{-1}$. Find the resultant velocity of the boat. If the breadth of the river is 100 m, find how far down the river will the boat reach the opposite bank.

}\SetValue{Concept}{%



}\SetValue{AltText}{%



}\SetValue{Solution}{%

We are given:

- The speed of the boat relative to the water: $8 \mathrm{~km} / \mathrm{h}$, directed straight across the river (i.e., perpendicular to the riverbanks).

- The speed of the river current: $6 \mathrm{~km} / \mathrm{h}$, flowing along the river (parallel to the banks).

- The breadth of the river: $100 \mathrm{~m}=0.1 \mathrm{~km}$

We are to find:

1. The resultant velocity of the boat (magnitude and direction).

2. The distance downstream (along the river) the boat reaches the opposite bank.

Step 1: Find the resultant velocity

This is a classic vector addition problem.

- The boat's velocity vector is perpendicular to the riverbanks:

$$
\vec{v}_{\text {boat }}=8 \mathrm{~km} / \mathrm{h}
$$

- The river's velocity vector is parallel to the bank:

$$
\vec{v}_{\text {river }}=6 \mathrm{~km} / \mathrm{h}
$$


These two vectors are perpendicular, so the resultant velocity $v_r$ is given by:

$$
v_r=\sqrt{8^2+6^2}=\sqrt{64+36}=\sqrt{100}=10 \mathrm{~km} / \mathrm{h}
$$


Step 2: Find the time to cross the river

Only the component across the river (i.e., the boat's own $8 \mathrm{~km} / \mathrm{h}$ speed) affects the time to cross the 100 m river.

$$
\text { Time }=\frac{\text { Distance }}{\text { Speed across }}=\frac{0.1 \mathrm{~km}}{8 \mathrm{~km} / \mathrm{h}}=0.0125 \mathrm{~h}
$$

Step 3: Find how far downstream the boat travels in that time

The river pulls the boat downstream at $6 \mathrm{~km} / \mathrm{h}$. So the downstream distance is:

Downstream distance $=6 \mathrm{~km} / \mathrm{h} \times 0.0125 \mathrm{~h}=0.075 \mathrm{~km}=$  75 m

Final Answers:

- Resultant velocity of the boat: $10 \mathrm{~km} / \mathrm{h}$

- Distance downstream from the starting point:
75 m

}\SetValue{Rubric}{%Markdown



}\SetValue{Hint}{%
Solution Goes Here
}\SetValue{Answer}{%

}
\ProcessDATA



