\SetValue{Module}{1}\SetValue{SectionAB}{A}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%%
    
Kwame and Yaro set out from school simultaneously. Kwame goes due north, and Yaro runs on a bearing of $047^{\circ}$. When Yaro has gone 550 m, the boys are 500 m apart. How far is Kwame from the school?

}\SetValue{Concept}{%



}\SetValue{AltText}{%



}\SetValue{Solution}{%

1. Define the Scenario:

- Let the school be point S.

- Kwame travels North. Let his position be point K. The distance from the school to Kwame is SK, which we denote as $x$ meters.

- Yaro travels on a bearing of $047^{\circ}$ (which is $47^{\circ}$ clockwise from North). Let his position be point Y. The distance from the school to Yaro is SY $=550$ meters.

- The distance between Kwame and Yaro is KY = 500 meters.

- The angle between Kwame's path (North) and Yaro's path $\left(047^{\circ}\right)$ is $\angle K S Y=47^{\circ}$.

2. Form the Triangle:

- The points $\mathrm{S}, \mathrm{K}$, and Y form a triangle, $\triangle S K Y$.

- We know the lengths of two sides ( $\mathrm{SY}=550, \mathrm{KY}=500$ ) and the angle between one known side (SY) and the unknown side ( $\mathrm{SK}=x$ ), which is $\angle K S Y=47^{\circ}$.

3. Apply the Law of Cosines:

- The Law of Cosines states that for any triangle with sides $a, b, c$, and the angle $C$ opposite side $c: c^2=a^2+b^2-2 a b \cos (C)$

- Applying this to $\triangle S K Y$ to relate the side KY to the other two sides and the angle $\angle K S Y$ :

$$
K Y^2=S K^2+S Y^2-2(S K)(S Y) \cos (\angle K S Y)
$$

4. Substitute Values and Solve the Equation:

- Substitute the known values into the equation:

$$
500^2=x^2+550^2-2(x)(550) \cos \left(47^{\circ}\right)
$$

- Calculate the squares and simplify:

$$
250000=x^2+302500-1100 x \cos \left(47^{\circ}\right)
$$

- Rearrange into a standard quadratic equation $\left(a x^2+b x+c=0\right)$ :

$$
\begin{gathered}
x^2-\left(1100 \cos \left(47^{\circ}\right)\right) x+(302500-250000)=0 \\
x^2-\left(1100 \cos \left(47^{\circ}\right)\right) x+52500=0
\end{gathered}
$$

- Use the approximate value $\cos \left(47^{\circ}\right) \approx 0.681998$ :

$$
\begin{gathered}
x^2-(1100 \times 0.681998) x+52500 \approx 0 \\
x^2-750.1978 x+52500 \approx 0
\end{gathered}
$$

5. Solve the Quadratic Equation (using the quadratic formula):

- The quadratic formula for $a x^2+b x+c=0$ is $x=\frac{-b \pm \sqrt{b^2-4 a c}}{2 a}$.

- Here, $a=1, b \approx-750.1978$, and $c=52500$.

$$
\begin{gathered}
x \approx \frac{-(-750.1978) \pm \sqrt{(-750.1978)^2-4(1)(52500)}}{2(1)} \\
x \approx \frac{750.1978 \pm \sqrt{562796.74-210000}}{2} \\
x \approx \frac{750.1978 \pm \sqrt{352796.74}}{2} \\
x \approx \frac{750.1978 \pm 593.9669}{2}
\end{gathered}
$$

6. Calculate the Two Possible Solutions:

- Solution 1:

$$
x_1 \approx \frac{750.1978+593.9669}{2}=\frac{1344.1647}{2} \approx 672.08
$$

- Solution 2:

$$
x_2 \approx \frac{750.1978-593.9669}{2}=\frac{156.2309}{2} \approx 78.12
$$


Therefore, based on the Law of Cosines, Kwame's distance from the school ( $x$ ) could be approximately 78.1 meters or approximately 672.1 meters. Both are valid mathematical solutions to the triangle described.

}\SetValue{Rubric}{%Markdown



}\SetValue{Hint}{%
Solution Goes Here
}\SetValue{Answer}{%

}
\ProcessDATA



