\SetValue{Module}{1}\SetValue{SectionAB}{A}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%%
    
After Euclid High School's last basketball game, it was determined that $\frac{1}{4}$ of the team's points were scored by Alexa and $\frac{2}{7}$ were scored by Brittany. Chelsea scored 15 points. None of the other 7 team members scored more than 2 points. What was the total number of points scored by the other 7 team members?

	\ansFIVEs{%start
		10}{%<--- (A)
		11 }{%<--- (B)
		12 }{%<--- (C)
		13 }{%<---- (D)
	14}%<---- (D)

}\SetValue{Concept}{%



}\SetValue{AltText}{%



}\SetValue{Solution}{%

The total number of points scored by players other than Alexa and Brittany was at least 15 and at most $15+7 \cdot 2=29$. The fraction of the team's points scored by those players was $1-\frac{1}{4}-\frac{2}{7}=\frac{13}{28}$, so the number of points that they scored was a multiple of 13 . The only multiple of 13 between 15 and 29 is 26 , so the number of points scored by the 7 players other than Alexa, Brittany, and Chelsea was $26-15=11$.

OR

The total number of points scored by the team was a multiple of both 4 and 7 and thus was a multiple of 28. If the total was 28, then Alexa scored 7 and Brittany scored 8, and so Chelsea could not have scored 15. If the total was $28 n$, where $n \geq 3$, then Alexa scored $7 n$ and Brittany scored $8 n$. With Chelsea scoring 15, this leaves $13 n-15 \geq 24$ points for the remaining 7 team members. But then at least one of them scored more than 2 points. So the only possible score was $28 \cdot 2=56$. Then Alexa scored 14, Brittany scored 16, Chelsea scored 15, and the remaining 7 team members scored a total of 11 points.
}\SetValue{Rubric}{%Markdown



}\SetValue{Hint}{%
Solution Goes Here
}\SetValue{Answer}{%
Answer (B)
}
\ProcessDATA



