\SetValue{Module}{1}\SetValue{SectionAB}{A}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%%
    
Nicolas is planning to send a package to his friend Anton, who is a stamp collector. To pay for the postage, Nicolas would like to cover the package with a large number of stamps. Suppose he has a collection of 5 -cent, 10 -cent, and 25 -cent stamps, with exactly 20 of each type. What is the greatest number of stamps Nicolas can use to make exactly $\$ 7.10$ in postage? (Note: The amount $\$ 7.10$ corresponds to 7 dollars and 10 cents. One dollar is worth 100 cents.)

\ansFIVEs{%start
		 45 }{%<--- (A)
		 46 }{%<--- (B)
		 51 }{%<--- (C)
		 54 }{%<---- (D)
		 55 }%<---- (D)
}\SetValue{Concept}{%

니콜라스는 우표 수집가인 친구 안톤에게 소포를 보낼 계획입니다. 우편 요금을 지불하기 위해 니콜라스는 많은 수의 우표로 패키지를 덮고 싶습니다. 그가 5센트, 10센트, 25센트 우표를 각 종류별로 정확히 20장씩 가지고 있다고 가정합니다. 니콜라스가 우편 요금으로 정확히 \$7.10을 벌기 위해 사용할 수 있는 우표의 최대 개수는 얼마인가요? (참고: \$7.10은 7달러와 10센트에 해당합니다. 1달러는 100센트의 가치가 있습니다.)

5-cent (nickels), 20개=1달러: 19개-0.95달러
10 cent (dimes), 10개-1달러 : 19개-1.9달러
25-cent (quarters). 4개-1달러: 17개-4.25달러

55

}\SetValue{AltText}{%



}\SetValue{Solution}{%

Let's use the most stamps to make 7.10. We have 20 of each stamp, 5-cent (nickels), 10 cent (dimes), and 25-cent (quarters).

If we want the highest number of stamps, we must have the highest number of the smaller value stamps (like the coins above). We can use 20 nickels and 20 dimes to bring our total cost to $7.10-3.00=4.10$. However, when we try to use quarters, the 25 cents don't fit evenly, so we have to give back 15 cents to make the quarter amount 4.25. The most efficient way to do this is to give back a 10 -cent (dime) stamp and a 5 -cent (nickel) stamp to have 38 stamps used so far. Now, we just use $\frac{425}{25}=17$ quarters to get a grand total of $38+17=(\mathbf{E}) 55$.
}\SetValue{Rubric}{%Markdown



}\SetValue{Hint}{%
Solution Goes Here
}\SetValue{Answer}{%

}
\ProcessDATA



