\SetValue{SectionAB}{}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%

\begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    $t$ 
    (seconds)
    & 0 & 60 & 90 & 120 & 135 & 150 \\
    \hline 
    $f(t)$  
    (gallons per second)
    & 0 & 0.1 & 0.15 & 0.1 & 0.05 & 0 \\
    \hline
    \end{tabular}

A customer at a gas station is pumping gasoline into a gas tank. The rate of flow of gasoline is modeled by a differentiable function $f$, where $f(t)$ is measured in gallons per second and $t$ is measured in seconds since pumping began. Selected values of $f(t)$ are given in the table.
       
Show the setup for your calculations.

(d) Using the model $g$ defined in part (c), find the value of $g^{\prime}(140)$. Interpret the meaning of your answer in the context of the problem.

}\SetValue{Solution}{%LaTeX

$\begin{aligned} & g^{\prime}(140) \approx-0.004908 \\ & g^{\prime}(140)=-0.005(\text { or }-0.004)\end{aligned}$

The rate at which gasoline is flowing into the tank is decreasing at a rate of 0.005 (or 0.004) gallon per second per second at time $t=140$ seconds.

}\SetValue{Rubric}{%Markdown

# General Scoring Notes

The model solution is presented using standard mathematical notation.
Answers (numeric or algebraic) need not be simplified. Answers given as a decimal approximation should be correct to three places after the decimal point. Within each individual free-response question, at most one point is not earned for inappropriate rounding.

| $t$ <br> (seconds) | 0 | 60 | 90 | 120 | 135 | 150 |
| :---: | :---: | :---: | :---: | :---: | :---: | :---: |
| $f(t)$ <br> (gallons per second) | 0 | 0.1 | 0.15 | 0.1 | 0.05 | 0 |

A customer at a gas station is pumping gasoline into a gas tank. The rate of flow of gasoline is modeled by a differentiable function $f$, where $f(t)$ is measured in gallons per second and $t$ is measured in seconds since pumping began. Selected values of $f(t)$ are given in the table.

## Model Solution (d)

$\begin{aligned} & g^{\prime}(140) \approx-0.004908 \\ & g^{\prime}(140)=-0.005(\text { or }-0.004)\end{aligned}$

The rate at which gasoline is flowing into the tank is decreasing at a rate of 0.005 (or 0.004) gallon per second per second at time $t=140$ seconds.

## Scoring (d)

- For $\begin{aligned} & g^{\prime}(140) \approx-0.004908 \\ & g^{\prime}(140)=-0.005(\text { or }-0.004)\end{aligned}$
        - $g'(140)$; 1 point

- For ``The rate at which gasoline is flowing into the tank is decreasing at a rate of 0.005 (or 0.004 ) gallon per second per second at time $t=140$ seconds."
        - Interpretation; 1 point

## Scoring notes (d)

- The exact value of $g^{\prime}(140)$ is $\frac{1}{500} \cos \left(\frac{49}{36}\right)-\frac{49}{9000} \sin \left(\frac{49}{36}\right)$.

- The value of $g^{\prime}(140)$ may appear only in the interpretation.

- To be eligible for the second point a response must present some numerical value for $g^{\prime}(140)$.

- To earn the second point the interpretation must include ``the rate of flow of gasoline is changing at a rate of [the declared value of $g^{\prime}(140)$]" and ``at $t=140$ " (or equivalent).

- An interpretation of ``decreasing at a rate of -0.005" or ``increasing at a rate of 0.005" does not earn the second point.

- Degree mode: In degree mode, $g^{\prime}(140)=0.001997$ or 0.00187.

Total for part (d) 2 points

}\SetValue{Answer}{%

}
\ProcessDATA


