\SetValue{SectionAB}{}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%

A bottle of milk is taken out of a refrigerator and placed in a pan of hot water to be warmed. The increasing function $M$ models the temperature of the milk at time $t$, where $M(t)$ is measured in degrees Celsius $\left({ }^{\circ} \mathrm{C}\right)$ and $t$ is the number of minutes since the bottle was placed in the pan. $M$ satisfies the differential equation $\frac{d M}{d t}=\frac{1}{4}(40-M)$. At time $t=0$, the temperature of the milk is $5^{\circ} \mathrm{C}$. It can be shown that $M(t)<40$ for all values of $t$.

(b) Use the line tangent to the graph of $M$ at $t=0$ to approximate $M(2)$, the temperature of the milk at time $t=2$ minutes.

}\SetValue{Solution}{%LaTeX

$\left.\frac{d M}{d t}\right|_{t=0}=\frac{1}{4}(40-5)=\frac{35}{4}$

The tangent line equation is $y=5+\frac{35}{4}(t-0)$.

$$
M(2) \approx 5+\frac{35}{4} \cdot 2=22.5
$$


The temperature of the milk at time $t=2$ minutes is approximately $22.5^{\circ}$ Celsius.

}\SetValue{Rubric}{%Markdown

# General Scoring Notes

The model solution is presented using standard mathematical notation.

Answers (numeric or algebraic) need not be simplified. Answers given as a decimal approximation should be correct to three places after the decimal point. Within each individual free-response question, at most one point is not earned for inappropriate rounding.

A bottle of milk is taken out of a refrigerator and placed in a pan of hot water to be warmed. The increasing function $M$ models the temperature of the milk at time $t$, where $M(t)$ is measured in degrees Celsius $\left({ }^{\circ} \mathrm{C}\right)$ and $t$ is the number of minutes since the bottle was placed in the pan. $M$ satisfies the differential equation $\frac{d M}{d t}=\frac{1}{4}(40-M)$. At time $t=0$, the temperature of the milk is $5^{\circ} \mathrm{C}$. It can be shown that $M(t)<40$ for all values of $t$.


## Model Solution (b)

$\left.\frac{d M}{d t}\right|_{t=0}=\frac{1}{4}(40-5)=\frac{35}{4}$

The tangent line equation is $y=5+\frac{35}{4}(t-0)$.

$$
M(2) \approx 5+\frac{35}{4} \cdot 2=22.5
$$


The temperature of the milk at time $t=2$ minutes is approximately $22.5^{\circ}$ Celsius.

## Scoring (b)

- For $\left.\frac{d M}{d t}\right|_{t=0}=\frac{1}{4}(40-5)=\frac{35}{4}$
    - $\left.\frac{d M}{d t}\right|_{t=0}$; 1 point

- For The tangent line equation is $y=5+\frac{35}{4}(t-0)$. 

$M(2) \approx 5+\frac{35}{4} \cdot 2=22.5$

The temperature of the milk at time $t=2$ minutes is approximately $22.5^{\circ}$ Celsius.
    - Approximation; 1 point
    
## Scoring notes (b)

- The value of the slope may appear in a tangent line equation or approximation.

- A response of $5+\frac{35}{4} \cdot 2$ is the minimal response to earn both points.

- A response of $\frac{1}{4}(40-5)$ earns the first point. If there are any subsequent errors in simplification, the response does not earn the second point.

- In order to earn the second point the response must present an approximation found by using a tangent line that:
    - passes through the point $(0,5)$ and
    - has slope $\frac{35}{4}$ or a nonzero slope that is declared to be the value of $\frac{d M}{d t}$.

- An unsupported approximation does not earn the second point.

- The approximation need not be simplified, but the response does not earn the second point if the approximation is simplified incorrectly.

Total for part (b) 2 points

}\SetValue{Answer}{%

}
\ProcessDATA


