\SetValue{SectionAB}{}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%

Pam is going to watch a movie on her television at home. She is going to watch the movie as it was shown in movie theaters, in its original aspect ratio of 1.85:1 (length:height). Her television has an aspect ratio of 4:3 and a length of 48 inches. If the movie takes up the entire length of her television screen, how many inches of screen height, to the nearest whole inch, will NOT be used on her TV screen to show the movie?

\ansFOURs{%start
10}{%<--- (A)
16}{%<--- (B)
22}{%<--- (C)
44}%<---- (D)

}\SetValue{Solution}{%
Answer: \textbf{(A)} 

We are given the following information:

\begin{itemize}
    \item The movie has an aspect ratio of 1.85:1 (length:height).
    \item Pam's TV has an aspect ratio of 4:3 (length:height).
    \item The length of Pam's TV is 48 inches.
    \item We need to determine how many inches of screen height will NOT be used.
\end{itemize}

 Step 1: Find the Heights of the Movie and the TV
 TV Height Calculation
The aspect ratio of the TV is 4:3, so the height of the TV is:

$
\text{TV height} = \frac{3}{4} \times 48 = 36 \text{ inches}
$

 Movie Height Calculation
The movie's aspect ratio is 1.85:1, so the height when displayed on the TV (using the full 48-inch length) is:

$
\text{Movie height} = \frac{48}{1.85} = 25.95 \approx 26 \text{ inches}
$

 Step 2: Find the Unused Height
The unused screen height is the difference between the TV height and the movie height:

$
\text{Unused height} = 36 - 26 = 10 \text{ inches}
$

 Step 3: Select the Correct Answer
The correct choice is $ A) 10 $ inches.

}\SetValue{Answer}{%
A
}
\ProcessDATA


