\SetValue{Module}{1}\SetValue{SectionAB}{A}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%%
    
Chloe and Zoe are both students in Ms. Demeanor's math class. Last night they each solved half of the problems in their homework assignment alone and then solved the other half together. Chloe had correct answers to only $80 \%$ of the problems she solved alone, but overall $88 \%$ of her answers were correct. Zoe had correct answers to $90 \%$ of the problems she solved alone. What was Zoe's overall percentage of correct answers?

\ansFIVEs{%start
		89 }{%<--- (A)
		92 }{%<--- (B)
		93 }{%<--- (C)
		96 }{%<---- (D)
		98 }%<---- (D)
}\SetValue{Concept}{%



}\SetValue{AltText}{%



}\SetValue{Solution}{%

Answer (C): For simplicity, suppose that the assignment contained 100 problems. Chloe correctly solved $80 \%$ of the 50 problems she worked on alone, which was 40 problems. She had a total of 88 correct answers, so $88-40=48$ of the 50 problems that she and Zoe worked on together had correct answers. In addition Zoe correctly solved $90 \%$ of the 50 problems that she worked on alone, which was 45 problems. Her overall percentage of correct answers was $45+48=93$.

OR

Chloe's percentage of success on the half that she solved alone was 80, which is 8 points less than 88. So her percentage of success on the other half was 8 points above 88, or 96. Zoe's percentage of success was 90 on half of the problems and 96 on the other half, so her overall percentage was the average of 90 and 96, which is 93.
}\SetValue{Rubric}{%Markdown



}\SetValue{Hint}{%
Solution Goes Here
}\SetValue{Answer}{%

}
\ProcessDATA



