\SetValue{SectionAB}{}\SetValue{MainChapter}{}\SetValue{SubChapter}{}\SetValue{Contents}{%

From 5 A.M. to 10 A.M., the rate at which vehicles arrive at a certain toll plaza is given by $A(t)=450 \sqrt{\sin (0.62 t)}$, where $t$ is the number of hours after 5 A.M. and $A(t)$ is measured in vehicles per hour. Traffic is flowing smoothly at 5 A.M. with no vehicles waiting in line.

(a) Write, but do not evaluate, an integral expression that gives the total number of vehicles that arrive at the toll plaza from 6 A.M. $(t=1)$ to 10 A.M. $(t=5)$.

}\SetValue{Solution}{%

The total number of vehicles that arrive at the toll plaza from 6 A.M. to 10 A.M. is given by $\int_1^5 A(t) d t$.

}\SetValue{Rubric}{%

# General Scoring Notes

The model solution is presented using standard mathematical notation.

Answers (numeric or algebraic) need not be simplified. Answers given as a decimal approximation should be correct to three places after the decimal point. Within each individual free-response question, at most one point is not earned for inappropriate rounding.

From 5 A.M. to 10 A.M., the rate at which vehicles arrive at a certain toll plaza is given by $A(t)=450 \sqrt{\sin (0.62 t)}$, where $t$ is the number of hours after 5 A.M. and $A(t)$ is measured in vehicles per hour. Traffic is flowing smoothly at 5 A.M. with no vehicles waiting in line.

## Model Solution (a)

The total number of vehicles that arrive at the toll plaza from 6 A.M. to 10 A.M. is given by $\int_1^5 A(t) d t$.

## Scoring (a)

- For The total number of vehicles that arrive at the toll plaza from 6 A.M. to 10 A.M. is given by $\int_1^5 A(t) d t$.
    - Answer; 1 point

## Scoring notes (a)

- The response must be a definite integral with correct lower and upper limits to earn this point.

- Because $|A(t)|=A(t)$ for $1 \leq t \leq 5$, a response of $\int_1^5|450 \sqrt{\sin (0.62 t)}| d t$ or $\int_1^5|A(t)| d t$ earns the point.

- A response missing $d t$ or using $d x$ is eligible to earn the point.

- A response with a copy error in the expression for $A(t)$ will earn the point only in the presence of $\int_1^5 A(t) d t$

Total for part (a) 1 points

}\SetValue{Answer}{%

}
\ProcessDATA


