\begin{GPTQ}
    What are major mistakes for this question?
    
\end{GPTQ}

\begin{GPTA}
When solving this problem, some common mistakes might include:  

1. Incorrect Calculation of the Cube's Volume:

- Forgetting to cube the edge length: Some may mistakenly use the formula for the volume of a square $\left(s^2\right)$ instead of a cube $\left(s^3\right)$.

- Arithmetic errors in calculating $68^3$, which is $68 \times 68 \times 68$.

2. Incorrect Calculation of the Sphere's Volume:

- Misusing the formula: The sphere's volume is calculated using $V=\frac{4}{3} \pi r^3$. Errors might occ ur by misapplying the formula, such as using $\frac{4}{3} \pi r^2$ (which is for surface area).

- Arithmetic mistakes or rounding errors when calculating $34^3$ and then multiplying by $\frac{4}{3} \pi$ -

3. Mistake in Subtracting Volumes:

- Failing to correctly subtract the sphere's volume from the cube's volume, which determines the volume of the space not occupied by the sphere.

- Not accurately performing subtraction or rounding errors.

4. Conceptual Errors:

- Assuming incorrect spatial relationships, such as believing the sphere completely fills the cu be or misunderstanding how the sphere is placed within the cube.

- Misinterpreting the question, such as by calculating only the volume of the sphere or cube ra ther than the empty space.

5. Incorrect Units:

- Not considering or mislabeling cubic inches in the final answer.

Being mindful of these potential errors and carefully applying formulas can help avoid mistakes in solvi ng this type of problem.



\end{GPTA}

